# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
1.Load data from activity.csv file

Make sure the activity.csv is at same directory with this rmd file.
```{r echo=TRUE}
data = read.csv("activity.csv")
```
2.Remove NA data , create a complete data set.
```{r echo=TRUE}
complete_data = data[complete.cases(data),]
complete_data$date = as.character(complete_data$date)
```

## What is mean total number of steps taken per day?
1.Make a histogram of the total number of steps taken each day
```{r echo=TRUE}
total_steps_byday = tapply(complete_data$steps,complete_data$date,sum)
hist(total_steps_byday,xlab="days")
```
2.Calculate the mean total number of steps taken per day
```{r echo=TRUE}
mean(total_steps_byday)
```
3.Calculate median total number of steps taken per day
```{r echo=TRUE}
median(total_steps_byday)
```

## What is the average daily activity pattern?
1.Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r echo=TRUE}
mean_steps_byinterval = tapply(complete_data$steps, complete_data$interval, mean)
plot(mean_steps_byinterval,type="l", xlab="5 minutes interval count", ylab="average number of steps")
```
2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r echo=TRUE}
mean_steps_byinterval[mean_steps_byinterval==max(mean_steps_byinterval)]
```

## Imputing missing values
1.Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r echo=TRUE}
dim(data)[1]-sum(complete.cases(data))
```
2.Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. 

Find NA status of data set.
```{r echo=TRUE}
summary(is.na(data$steps))
summary(is.na(data$date))
summary(is.na(data$interval))
```
So I only need fill missing steps of original data set.I use average steps of interval to fill to missing steps with same interval.
3.Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r echo=TRUE}
filling_data = data
for (i in 1:nrow(filling_data)){
  if(is.na(filling_data$steps[i])){
    filling_data$steps[i] = mean_steps_byinterval[as.character(filling_data$interval[i])]
  }
}
```
4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 
```{r echo=TRUE}
total_steps_byday = tapply(filling_data$steps,filling_data$date,sum)
hist(total_steps_byday,xlab="days")
mean(total_steps_byday)
median(total_steps_byday)
```

## Are there differences in activity patterns between weekdays and weekends?
1.Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r echo=TRUE}
days = as.POSIXct(strptime(filling_data$date,format="%Y-%m-%d"))
days = as.POSIXlt(days)$wday
for(i in 1:length(days)){
  if(days[i]==0 | days[i]==6){
    days[i] = "weekend"
  }else{
    days[i] = "weekday"
  }
}
days = as.factor(days)
filling_data$weekday = days
```
2.Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).
```{r echo=TRUE}
mean_steps_weekdays_byinterval = with(filling_data, tapply(steps, list(weekday,interval), mean))
par(mfrow =c(2,1))
plot(mean_steps_weekdays_byinterval[1,],type="l",xlab="interval",ylab="number of steps",main="weekday")
plot(mean_steps_weekdays_byinterval[2,],type="l",xlab="interval",ylab="number of steps",main="weekend")
```
